Invasive chameleons released from predation display more conspicuous colors

### 2021-08-24 supp.Rmd
Making supp fixes, checking the table S1 rendering given it has been updated

Correspondance: Martin J. Whiting  
Email: Martin.Whiting@mq.edu.au

@@

We provide an expanded table of hypotheses and associated predictions. We also identify the data needed to test these predictions.

```{r tablehyp, tab.cap = "Hypotheses and associated predictions tested in this paper in relation to the population of interest, the receiver visual system used in visual modelling, and the background against which the contrast of the signal was calculated for chromatic and luminance contrast."}
  source("./R/func.R") 
  hyp <-  read.csv(file = "./output/tables/Table_hyp_pred.csv")

>>>>

Correspondance: Martin J. Whiting  
Email: martin.whiting@mq.edu.au

@@

We provide an expanded table of the key hypothesis and associated predictions. We also identify the data needed to test these predictions.

```{r tablehyp, tab.cap = "Hypothesis and associated predictions tested in this paper in relation to the population of interest, the receiver visual system used in visual modelling, and the background against which the contrast of the signal was calculated for chromatic and luminance contrast."}
  source("./R/func.R") 
  hyp <-  read.csv(file = "./output/tables/Table_hyp_pred.csv")
